A Lyapunov Analysis of Momentum Methods \\ in Optimization

### 2016-11-08 Draft14.tex
small edits

\section{Momentum Methods}
\label{Sec:MomLyap}
In this section, we introduce two families of momentum dynamics, both which are generated by functionals defined on continuous-time curves. We illustrate how to derive a Lyapunov function from these dynamics. Next, we show how these dynamics can be discretized to obtain optimization algorithms. The same discrete-time mappings can be applied to the Lyapunov function, resulting in a tool which can be used to analyze the discrete-time algorithms. We provide examples of this procedure for the quasi-monotone subgradient algorithm, accelerated gradient descent, the conditional gradient algorithm, and several other novel algorithms. 
 \subsection{Lyapunov Analysis}
We study dynamics that are based on the Euler-Lagrange equation \eqref{Eq:ELBreg} in the setting where the ideal scaling~\eqref{Eq:IdeScaBet} holds with equality~$\dot \beta_t = e^{\alpha_t}$. Notice, now the entire Bregman Lagrangian is parameterized by $\beta_t$, which determines the convergence rate:
 \begin{subequations}\label{Eq:EL}
 \begin{align}
 Z_t &= X_t + \frac{1}{\dot \beta_t} \dot X_t \label{Eq:ELZ},\\
 \frac{d}{dt}\nabla h(Z_t) &= -\dot \beta_t e^{\beta_t} \nabla f(X_t)\label{Eq:ELH}.
 \end{align}
 \end{subequations}
We begin by demonstrating how to derive the Lyapunov function~\eqref{Eq:E} for the momentum dynamics~\eqref{Eq:EL}; this derivation is similar in spirit to the Lyapunov analysis of mirror descent by Nemirovski and Yudin.

%\begin{small}
\begin{subequations}\label{Eq:LyapAnal}
\begin{align}
 \frac{d}{dt}D_h\left(x, Z_t\right)  &= \frac{d}{dt}\left( h(x) - h(Z_t) - \langle \nabla h(Z_t), x- Z_t\rangle\right)  \notag\\
& = - \langle \nabla h(Z_t), \dot Z_t\rangle -\left\langle \frac{d}{dt} \nabla h(Z_t),x - Z_t\right\rangle  + \langle \nabla h(Z_t), \dot Z_t\rangle \notag\\ 
 &= -\left\langle \frac{d}{dt} \nabla h\left(Z_t\right), x - Z_t\right\rangle \, \notag\\%\label{eq:apply-identity}\\
&=   \dot \beta_t e^{\beta_t}\left\langle\nabla f(X_t), x  - X_{t} - \frac{1}{\dot \beta_t} \dot X_{s} \right\rangle  \, \label{eq:apply-dynamics}   \\
& =   \dot \beta_t e^{\beta_t} \langle \nabla f(X_t), x - X_t \rangle\, - e^{ \beta_t} \langle \nabla f(X_t), \dot X_t\rangle dt\, \notag   \\
& = \dot \beta_t e^{\beta_t} \langle \nabla f(X_t), x - X_t \rangle\,  -   \frac{d}{dt}\left(e^{ \beta_t} f(X_t)\right)\,   + \dot \beta_t e^{\beta_t}  f(X_t)  \notag\\
&= \dot \beta_t e^{\beta_t} [f(X_t)+ \langle \nabla f(X_t), x - X_t \rangle] -\frac{d}{dt}\left(e^{ \beta_t} f(X_t)\right)\,  \notag  \\ %\label{Eq:Line9}\\
& \leq  \dot \beta_t e^{\beta_t}f(x) - \frac{d}{dt}\left(e^{ \beta_t} f(X_t)\right)\, \label{eq:apply-convexity}\\
& = - \frac{d}{dt} \left(e^{\beta_t}\left(f(X_t) - f(x)\right)\right) \label{Eq:cond1}.
\end{align}
\end{subequations}
%\end{small}
Here~\eqref{eq:apply-dynamics} uses the momentum dynamics%~\eqref{Eq:EL}.
~\eqref{Eq:ELH} and~\eqref{Eq:ELZ}. 
The inequality~\eqref{eq:apply-convexity} follows from the convexity of $f$. Rearranging terms and taking $x = x^\ast$, we have shown that the function~\eqref{Eq:E} has nonpositive derivative for all $t$ and is hence a Lyapunov function for the family of momentum dynamics~\eqref{Eq:EL}.

@@

\mathcal{L}(x, \dot x, t) = \dot \beta_t e^{2\beta_t} \left(\frac{\mu}{2}\left\|\frac{\dot x}{\dot \beta_t}\right\|^2 - f(x)\right),

@@

and that this Lagrangian can be generalized to include non-Euclidean geometries; however, further exploration of this Lagrangian is outside the scope of this work. Here, we demonstrate that~\eqref{Eq:StrongLyap} can be used to show an $O(e^{-\beta_t})$ rate of convergence for~\eqref{Eq:StrongDyn} with a strong convexity assumption. To do so, note that if we can ensure  $\dot \E_t = e^{\beta_t}\dot \beta_t \tilde{\E}_t + e^{\beta_t} \dot{\tilde{\E}}_t \leq 0$, which amounts to ensuring

@@

\tilde E_{k+1} \leq \Big(1-\tfrac{1}{\sqrt{\kappa}}\Big) \tilde  E_k, 

@@

A_{k}\left(f(x_{k}) - \frac{1}{A_{k}}D_h(x, z_{k})\right) &\leq (A_k -  A_0) f(x) + \left(f(x_0)+ \frac{1}{A_0}  D_h(x^\ast, z_0)\right) \notag \\

@@

%
%
%
\subsubsection{Conditional Gradient Method} 
\paragraph{Continuous-time Estimate Sequence}
For the conditional gradient method, the algorithm simply needed to ensure,
\begin{align}\label{Eq:InEq4}
0 &\leq \int_0^t\dot \beta_t e^{\beta_t}  [f(X_s)+ \langle \nabla f(X_s), x - X_s \rangle] -  \frac{d}{ds}\left\{ e^{ \beta_s}  f(X_s)\right\}\,ds.
\end{align}
 We can write~\eqref{Eq:InEq4} as, 
\begin{align*}
e^{ \beta_t}  f(X_t) \leq \int_0^t\dot \beta_t e^{\beta_t}  [f(X_s)+ \langle \nabla f(X_s), x - X_s \rangle]ds   + e^{\beta_0} f(X_0),
\end{align*}
and from the derivation of the Lypaynov function, we can conclude
\begin{align*}
e^{\beta_t} f(X_t) \leq  (e^{\beta_t} - e^{\beta_0}) f(x) + e^{\beta_0}f(X_0).
\end{align*}
Thus, $\{f(X_t),e^{\beta_t}\}$ is a continuous-time estimate sequence for this method. In Appendix~\ref{App:EstSeq}, we show the equivalence in discrete time between estimate sequences and our Lyapunov framework in this setting.
%

%
%
\subsection{Accelerated Gradient Strong Convexity}
Notice that for the dynamic~\eqref{Eq:StrongDyn}, the following holds:
\begin{align}\label{Eq:Strong}
 \frac{d}{dt}\left(e^{\beta_t}\frac{\mu}{2} \|x - Z_t\|^2\right)\, &=  \dot \beta_t e^{\beta_t} \frac{\mu}{2} \|x - Z_t\|^2 - e^{\beta_t} \mu\langle \dot Z_t, x - Z_t\rangle \notag\\
 &=  \dot \beta_t e^{\beta_t} \frac{\mu}{2} \|x - Z_t\|^2 + e^{\beta_t} \mu\langle \dot X_t, x - Z_t\rangle  + \dot  \beta_t e^{\beta_t} \left\langle \nabla f(X_t), x - X_t - \frac{1}{\dot \beta_t} \dot X_t\right\rangle \notag \\
  &=\dot  \beta_t e^{\beta_t} \frac{\mu}{2} \|x - Z_t\|^2 + \dot \beta_te^{\beta_t} \mu\langle  Z_t - X_t, x - X_t \rangle - \dot \beta_te^{\beta_t} \frac{\mu}{2}\| Z_t - X_t\|^2 \notag\\
 &\quad + \dot \beta_t e^{\beta_t} \langle \nabla f(X_t), x - X_t \rangle  - e^{\beta_t} \langle \nabla f(X_t),\dot X_t\rangle \notag\\
 & =  \dot \beta_t e^{\beta_t} \frac{\mu}{2} \|x - X_t\|^2 + \dot \beta_t e^{\beta_t} \langle \nabla f(X_t), x - X_t \rangle   - e^{\beta_t} \langle \nabla f(X_t),\dot X_t\rangle \notag \\
 %&\quad  - \left(\frac{1}{\dot \beta_s} - \dot \beta_s\right)e^{\beta_s} \frac{\mu}{2}\| \dot X_s\|^2\\
 &=   \dot \beta_t e^{\beta_t}\left( f(X_t) + \langle \nabla f(X_t), x - X_t \rangle+ \frac{\mu}{2} \|x - X_t\|^2\right)   -  \frac{d}{dt}\left( e^{ \beta_t}  f(X_t)\right),
\end{align}
where the the second to last line follows from completing the square.\footnote{We remark also that this derivation also shows how to derive the Lyapunov function~\eqref{Eq:StrongLyap} from the dynamic~\eqref{Eq:StrongDyn}.} %and choosing $\dot \beta_t^2 \leq 1$\footnote{The residual $e^{\beta_t}\frac{\mu \dot \beta_t}{2}\left(\frac{1}{\dot \beta_t^2} - 1\right)$ is the same as the residual term~\eqref{Eq:StrongResid} in the discrete-time setting (where $\dot \beta_t$ is discretized into the sequence $\{\tau_k\}_{k=1}^\infty$), except that it is scaled by an additional $e^{\beta_t}$. We dropped the exponential scaling in the discrete-time energy functional for simplicity.}
 Integrating both sides results in the following inequality, 
\begin{align*}
e^{\beta_t} f(X_t) + e^{\beta_t}\frac{\mu}{2} \|x - Z_t\|^2 &\leq \int_0^t\dot \beta_t e^{\beta_t}[ f(X_s)+ \langle \nabla f(X_s), x - X_s \rangle+ \frac{\mu}{2} \|x - X_s\|^2]\, ds\\
& \quad+ e^{\beta_0}f(X_0) + e^{\beta_0}\frac{\mu}{2} \|x - X_0\|^2.
\end{align*}
Therefore, 
\begin{align*}
e^{\beta_t} f(X_t) + e^{\beta_t}\frac{\mu}{2} \|x - Z_t\|^2 \leq (e^{\beta_t} - e^{\beta_0}) f(x) + e^{\beta_0}  f(X_0) + e^{\beta_0} \frac{\mu}{2} \|x - Z_0\|^2.
\end{align*}
and hence \begin{align*}
\{f(X_t) + \frac{\mu}{2} \|x - Z_t\|^2, e^{\beta_t}\},
\end{align*}
is a continuous-time estimate sequence. In Appendix~\ref{App:EstSeq}, we show the equivalence in discrete time between estimate sequences and our Lyapunov framework in this setting.

@@

%
  %%%%%%%%%%%%%%%%%
    \section{Momentum Algorithms}
        \label{App:Momentum}
\subsection{Proof of Theorem~\ref{Thm:Quasi}}
\label{App:ProofQuasi}
We use the Lyapunov function 
\begin{equation*}
E_k = A_k (f(x_k) - f(x^\ast)) + D_h(x^\ast, z_k)
\end{equation*}
to obtain a convergence guarantee for the quasi-monotone subgradient method~\eqref{Eq:QuasiSub}.
Denoting $D^\ast_{k+1, k} = D_h(x^\ast,z_{k+1})- D_h(x^\ast,z_{k})$, observe that
%\label{App:ProofQuasi}
%\begin{small}
\begin{subequations}
\begin{align}
D^\ast_{k+1, k}  &= -D_h(z_{k+1}, z_k) +  \langle \nabla h(z_{k+1}) - \nabla h(z_k), z_{k+1} - x^\ast\rangle \label{Eq:Mirror}\\
&\overset{\eqref{Eq:XSeqQuasi}}{\leq} -\frac{1}{2}\|z_k - z_{k+1}\|^2 -(A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_{k+1} - x^\ast\rangle \label{Eq:StrongConvAssump1} \\
&= -\frac{1}{2}\|z_k - z_{k+1}\|^2 - (A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_{k+1} - z_k\rangle -(A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_k - x^\ast\rangle \notag\\
&\leq\frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 - (A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_k - x^\ast\rangle \label{Eq:HoldBound1}\\
& \overset{\eqref{Eq:ZSeqQuasi}}{=}\frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 - (A_{k+1} - A_k) \left\langle \nabla f(x_{k+1}), \frac{A_{k+1}}{(A_{k+1} -A_{k})}(x_{k+1} - x_k) + x_k - x^\ast\right\rangle \notag \\
& =\frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2- A_{k+1} \left\langle \nabla f(x_{k+1}), x_{k+1} - x_k\right\rangle - (A_{k+1} -A_{k})\langle \nabla f(x_{k+1}), x_{k+1} - x^\ast\rangle \notag\\
&\quad + (A_{k+1} -A_{k})\langle \nabla f(x_{k+1}), x_{k+1} - x_k \rangle \notag\\
& = \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2- A_{k} \langle \nabla f(x_{k+1}), x_{k+1} - x_k\rangle  - (A_{k+1} -A_{k})\langle \nabla f(x_{k+1}), x_{k+1} - x^\ast\rangle. \notag\\
&\leq -A_k(f(x_{k+1}) - f(x_k)) - (A_{k+1} -A_{k})(f(x_{k+1}) - f(x^\ast)) + \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 \notag\\
& = A_k (f(x_k) - f(x^\ast)) - A_{k+1}(f(x_{k+1}) - f(x^\ast)) + \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 \notag
\end{align}
\end{subequations}
%\end{small}
where \eqref{Eq:StrongConvAssump1} follows from the strong convexity assumption on $h$, and \eqref{Eq:HoldBound1} uses the Fenchel-Young inequality. Thus, we obtain the following bound,
\begin{subequations}
\begin{align*}
E_{k+1} - E_k &\leq  \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2. 
\end{align*}
\end{subequations}
%Choosing $\sum_{i=0}^k (A_{i+1} -A_{i})^2  < \infty$ gives the convergence rate
%%\begin{align*}
%%E_{k} \leq E_0 + \frac{1}{2}\sum_{i=0}^{k} (A_{i+1} -A_{i})^2 \|\nabla f(x_{i})\|_\ast^2,
%%\end{align*}
%%which we can write as
%\begin{align}\label{Eq:ConvQuasi}
%f(x_k) - f(x^\ast) \leq \frac{D_h(x^\ast , x_0) +A_0 (f(x_0) - f(x^\ast)) + \frac{1}{2}\sum_{i=0}^{k} (A_{i+1} -A_{i})^2\|\nabla f(x_{i})\|_\ast^2}{A_k}.
%\end{align}

>>>>

\section{Momentum Methods}
\label{Sec:MomLyap}
In this section, we introduce two families of momentum dynamics, both which are generated by functionals defined on continuous-time curves. We illustrate how to derive a Lyapunov function from these dynamics. Next, we show how these dynamics can be discretized to obtain optimization algorithms. The same discrete-time mappings can be applied to the Lyapunov function, resulting in a tool which can be used to analyze the discrete-time algorithms. We provide examples of this procedure for the quasi-monotone subgradient algorithm, accelerated gradient descent, the conditional gradient algorithm, and several other novel algorithms. 
 \subsection{Lyapunov Analysis}
We study dynamics that are based on the Euler-Lagrange equation \eqref{Eq:ELBreg} in the setting where the ideal scaling~\eqref{Eq:IdeScaBet} holds with equality~$\dot \beta_t = e^{\alpha_t}$. Notice, now the entire Bregman Lagrangian is parameterized by $\beta_t$, which determines the convergence rate:
 \begin{subequations}\label{Eq:EL}
 \begin{align}
 Z_t &= X_t + \frac{1}{\dot \beta_t} \dot X_t \label{Eq:ELZ},\\
 \frac{d}{dt}\nabla h(Z_t) &= -\dot \beta_t e^{\beta_t} \nabla f(X_t)\label{Eq:ELH}.
 \end{align}
 \end{subequations}
We begin by demonstrating how to derive the Lyapunov function~\eqref{Eq:E} for the momentum dynamics~\eqref{Eq:EL}; this derivation is similar in spirit to the Lyapunov analysis of mirror descent by Nemirovski and Yudin. We first point the following nice identity, 
\begin{subequations}
\begin{align}
 \frac{d}{dt}D_h\left(x, Z_t\right)  &= \frac{d}{dt}\left( h(x) - h(Z_t) - \langle \nabla h(Z_t), x- Z_t\rangle\right)  \notag\\
& = - \langle \nabla h(Z_t), \dot Z_t\rangle -\left\langle \frac{d}{dt} \nabla h(Z_t),x - Z_t\right\rangle  + \langle \nabla h(Z_t), \dot Z_t\rangle \notag\\ 
 &= -\left\langle \frac{d}{dt} \nabla h\left(Z_t\right), x - Z_t\right\rangle. \, \notag%\label{eq:apply-identity}\\
 \end{align*}
 \end{subequations}
  Using this identity, we have the following argument:
%\begin{small}
\begin{subequations}\label{Eq:LyapAnal}
\begin{align}
 \frac{d}{dt}D_h\left(x, Z_t\right)  %&= \frac{d}{dt}\left( h(x) - h(Z_t) - \langle \nabla h(Z_t), x- Z_t\rangle\right)  \notag\\
%& = - \langle \nabla h(Z_t), \dot Z_t\rangle -\left\langle \frac{d}{dt} \nabla h(Z_t),x - Z_t\right\rangle  + \langle \nabla h(Z_t), \dot Z_t\rangle \notag\\ 
 &= -\left\langle \frac{d}{dt} \nabla h\left(Z_t\right), x - Z_t\right\rangle \, \notag\\%\label{eq:apply-identity}\\
&=   \dot \beta_t e^{\beta_t}\left\langle\nabla f(X_t), x  - X_{t} - \frac{1}{\dot \beta_t} \dot X_{s} \right\rangle  \, \label{eq:apply-dynamics}   \\
& =   \dot \beta_t e^{\beta_t} \langle \nabla f(X_t), x - X_t \rangle\, - e^{ \beta_t} \langle \nabla f(X_t), \dot X_t\rangle dt\, \notag   \\
& = \dot \beta_t e^{\beta_t} \langle \nabla f(X_t), x - X_t \rangle\,  -   \frac{d}{dt}\left(e^{ \beta_t} f(X_t)\right)\,   + \dot \beta_t e^{\beta_t}  f(X_t)  \notag\\
&= \dot \beta_t e^{\beta_t} [f(X_t)+ \langle \nabla f(X_t), x - X_t \rangle] -\frac{d}{dt}\left(e^{ \beta_t} f(X_t)\right)\,  \notag  \\ %\label{Eq:Line9}\\
& \leq  \dot \beta_t e^{\beta_t}f(x) - \frac{d}{dt}\left(e^{ \beta_t} f(X_t)\right)\, \label{eq:apply-convexity}\\
& = - \frac{d}{dt} \left(e^{\beta_t}\left(f(X_t) - f(x)\right)\right) \label{Eq:cond1}.
\end{align}
\end{subequations}
%\end{small}
Here~\eqref{eq:apply-dynamics} uses the momentum dynamics%~\eqref{Eq:EL}.
~\eqref{Eq:ELH} and~\eqref{Eq:ELZ}. 
The inequality~\eqref{eq:apply-convexity} follows from the convexity of $f$. Rearranging terms and taking $x = x^\ast$, we have shown that the function~\eqref{Eq:E} has nonpositive derivative for all $t$ and is hence a Lyapunov function for the family of momentum dynamics~\eqref{Eq:EL}.

@@

\mathcal{L}(x, \dot x, t) = e^{\gamma_t + \beta_t - \alpha_t}  \left(\frac{\mu}{2}\left\|\dot x\right\|^2 - f(x)\right),

@@

under the same ideal scaling conditions~\eqref{Eq:IdeSca}, where we take $e^{\alpha_t} = \dot \beta_t$. Furthermore, this Lagrangian can be generalized to include non-Euclidean geometries; however, further exploration of this Lagrangian is outside the scope of this work. Here, we demonstrate that~\eqref{Eq:StrongLyap} can be used to show an $O(e^{-\beta_t})$ rate of convergence for~\eqref{Eq:StrongDyn} with a strong convexity assumption. To do so, note that if we can ensure  $\dot \E_t = e^{\beta_t}\dot \beta_t \tilde{\E}_t + e^{\beta_t} \dot{\tilde{\E}}_t \leq 0$, which amounts to ensuring

@@

\tilde E_{k+1} \leq \left(1-\tfrac{1}{\sqrt{\kappa}}\right) \tilde  E_k, 

@@

A_{k}\left(f(x_{k}) - \frac{1}{A_{k}}D_h(x, z_{k})\right) &\leq (A_k -  A_0) f(x) + A_0\left(f(x_0)+ \frac{1}{A_0}  D_h(x^\ast, z_0)\right) \notag \\

@@

%
%
%
\subsubsection{Conditional Gradient Method} 
\paragraph{Continuous-time Estimate Sequence}
For the conditional gradient method, the algorithm simply needed to ensure,
\begin{align}\label{Eq:InEq4}
0 &\leq \int_0^t\dot \beta_t e^{\beta_t}  [f(X_s)+ \langle \nabla f(X_s), x - X_s \rangle] -  \frac{d}{ds}\left( e^{ \beta_s}  f(X_s)\right)\,ds.
\end{align}
 We can write~\eqref{Eq:InEq4} as, 
\begin{align*}
e^{ \beta_t}  f(X_t) \leq \int_0^t\dot \beta_t e^{\beta_t}  [f(X_s)+ \langle \nabla f(X_s), x - X_s \rangle]ds   + e^{\beta_0} f(X_0),
\end{align*}
and from the derivation of the Lypaynov function, we can conclude
\begin{align*}
e^{\beta_t} f(X_t) \leq  (e^{\beta_t} - e^{\beta_0}) f(x) + e^{\beta_0}f(X_0).
\end{align*}
Thus, $\{f(X_t),e^{\beta_t}\}$ is a continuous-time estimate sequence for this method. In Appendix~\ref{App:EstSeq}, we show the equivalence in discrete time between estimate sequences and our Lyapunov framework in this setting.
%

%
%
\subsection{Accelerated Gradient Strong Convexity}
Notice that for the dynamic~\eqref{Eq:StrongDyn}, the following holds:
\begin{align}\label{Eq:Strong}
 \frac{d}{dt}\left(e^{\beta_t}\frac{\mu}{2} \|x - Z_t\|^2\right)\, &=  \dot \beta_t e^{\beta_t} \frac{\mu}{2} \|x - Z_t\|^2 - e^{\beta_t} \mu\langle \dot Z_t, x - Z_t\rangle \notag\\
 &=  \dot \beta_t e^{\beta_t} \frac{\mu}{2} \|x - Z_t\|^2 + e^{\beta_t} \mu\langle \dot X_t, x - Z_t\rangle  + \dot  \beta_t e^{\beta_t} \left\langle \nabla f(X_t), x - X_t - \frac{1}{\dot \beta_t} \dot X_t\right\rangle \notag \\
  &=\dot  \beta_t e^{\beta_t} \frac{\mu}{2} \|x - Z_t\|^2 + \dot \beta_te^{\beta_t} \mu\langle  Z_t - X_t, x - X_t \rangle - \dot \beta_te^{\beta_t} \frac{\mu}{2}\| Z_t - X_t\|^2 \notag\\
 &\quad + \dot \beta_t e^{\beta_t} \langle \nabla f(X_t), x - X_t \rangle  - e^{\beta_t} \langle \nabla f(X_t),\dot X_t\rangle \notag\\
 & =  \dot \beta_t e^{\beta_t} \frac{\mu}{2} \|x - X_t\|^2 + \dot \beta_t e^{\beta_t} \langle \nabla f(X_t), x - X_t \rangle   - e^{\beta_t} \langle \nabla f(X_t),\dot X_t\rangle \notag \\
 %&\quad  - \left(\frac{1}{\dot \beta_s} - \dot \beta_s\right)e^{\beta_s} \frac{\mu}{2}\| \dot X_s\|^2\\
 &=   \dot \beta_t e^{\beta_t}\left( f(X_t) + \langle \nabla f(X_t), x - X_t \rangle+ \frac{\mu}{2} \|x - X_t\|^2\right)   -  \frac{d}{dt}\left( e^{ \beta_t}  f(X_t)\right),
\end{align}
where the the second to last line follows from completing the square.\footnote{We remark also that this derivation also shows how to derive the Lyapunov function~\eqref{Eq:StrongLyap} from the dynamic~\eqref{Eq:StrongDyn}.} %and choosing $\dot \beta_t^2 \leq 1$\footnote{The residual $e^{\beta_t}\frac{\mu \dot \beta_t}{2}\left(\frac{1}{\dot \beta_t^2} - 1\right)$ is the same as the residual term~\eqref{Eq:StrongResid} in the discrete-time setting (where $\dot \beta_t$ is discretized into the sequence $\{\tau_k\}_{k=1}^\infty$), except that it is scaled by an additional $e^{\beta_t}$. We dropped the exponential scaling in the discrete-time energy functional for simplicity.}
 Integrating both sides results in the following inequality, 
\begin{align*}
e^{\beta_t} f(X_t) + e^{\beta_t}\frac{\mu}{2} \|x - Z_t\|^2 &\leq \int_0^t\dot \beta_t e^{\beta_t}[ f(X_s)+ \langle \nabla f(X_s), x - X_s \rangle+ \frac{\mu}{2} \|x - X_s\|^2]\, ds\\
& \quad+ e^{\beta_0}f(X_0) + e^{\beta_0}\frac{\mu}{2} \|x - X_0\|^2.\\
&\leq \int_0^t\dot \beta_t e^{\beta_t}f(x) \,ds+ e^{\beta_0}f(X_0) + e^{\beta_0}\frac{\mu}{2} \|x - X_0\|^2.
\end{align*}
Therefore, 
\begin{align*}
e^{\beta_t} f(X_t) + e^{\beta_t}\frac{\mu}{2} \|x - Z_t\|^2 \leq (e^{\beta_t} - e^{\beta_0}) f(x) + e^{\beta_0}  f(X_0) + e^{\beta_0} \frac{\mu}{2} \|x - Z_0\|^2.
\end{align*}
and hence \begin{align*}
\{f(X_t) + \frac{\mu}{2} \|x - Z_t\|^2, e^{\beta_t}\},
\end{align*}
is a continuous-time estimate sequence. In Appendix~\ref{App:EstSeq}, we show the equivalence in discrete time between estimate sequences and our Lyapunov framework in this setting.

@@

%
  %%%%%%%%%%%%%%%%%
    \section{Momentum Algorithms}
        \label{App:Momentum}
\subsection{Proof of Theorem~\ref{Thm:Quasi}}
\label{App:ProofQuasi}
We use the Lyapunov function 
\begin{equation*}
E_k = A_k (f(x_k) - f(x^\ast)) + D_h(x^\ast, z_k)
\end{equation*}
to obtain a convergence guarantee for the quasi-monotone subgradient method~\eqref{Eq:QuasiSub}.
Denoting $D^\ast_{k+1, k} = D_h(x^\ast,z_{k+1})- D_h(x^\ast,z_{k})$, observe that
%\label{App:ProofQuasi}
%\begin{small}
\begin{subequations}
\begin{align}
D^\ast_{k+1, k}  &= -D_h(z_{k+1}, z_k) +  \langle \nabla h(z_{k+1}) - \nabla h(z_k), z_{k+1} - x^\ast\rangle \label{Eq:Mirror}\\
&\overset{\eqref{Eq:XSeqQuasi}}{\leq} -\frac{1}{2}\|z_k - z_{k+1}\|^2 -(A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_{k+1} - x^\ast\rangle \label{Eq:StrongConvAssump1} \\
&= -\frac{1}{2}\|z_k - z_{k+1}\|^2 - (A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_{k+1} - z_k\rangle -(A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_k - x^\ast\rangle \notag\\
&\leq\frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 - (A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_k - x^\ast\rangle \label{Eq:HoldBound1}\\
& \overset{\eqref{Eq:ZSeqQuasi}}{=}\frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 - (A_{k+1} - A_k) \left\langle \nabla f(x_{k+1}), \frac{A_{k+1}}{(A_{k+1} -A_{k})}(x_{k+1} - x_k) + x_k - x^\ast\right\rangle \notag \\
& =\frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2- A_{k+1} \left\langle \nabla f(x_{k+1}), x_{k+1} - x_k\right\rangle - (A_{k+1} -A_{k})\langle \nabla f(x_{k+1}), x_{k+1} - x^\ast\rangle \notag\\
&\quad + (A_{k+1} -A_{k})\langle \nabla f(x_{k+1}), x_{k+1} - x_k \rangle \notag\\
& = \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2- A_{k} \langle \nabla f(x_{k+1}), x_{k+1} - x_k\rangle  - (A_{k+1} -A_{k})\langle \nabla f(x_{k+1}), x_{k+1} - x^\ast\rangle. \notag\\
&\leq A_k(f(x_{k}) - f(x_{k+1})) - (A_{k+1} -A_{k})(f(x_{k+1}) - f(x^\ast)) + \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 \notag\\
& = A_k (f(x_k) - f(x^\ast)) - A_{k+1}(f(x_{k+1}) - f(x^\ast)) + \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 \notag
\end{align}
\end{subequations}
%\end{small}
where \eqref{Eq:StrongConvAssump1} follows from the strong convexity assumption on $h$, and \eqref{Eq:HoldBound1} uses the Fenchel-Young inequality. Thus, we obtain the following bound,
\begin{subequations}
\begin{align*}
E_{k+1} - E_k &\leq  \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2. 
\end{align*}
\end{subequations}
%Choosing $\sum_{i=0}^k (A_{i+1} -A_{i})^2  < \infty$ gives the convergence rate
%%\begin{align*}
%%E_{k} \leq E_0 + \frac{1}{2}\sum_{i=0}^{k} (A_{i+1} -A_{i})^2 \|\nabla f(x_{i})\|_\ast^2,
%%\end{align*}
%%which we can write as
%\begin{align}\label{Eq:ConvQuasi}
%f(x_k) - f(x^\ast) \leq \frac{D_h(x^\ast , x_0) +A_0 (f(x_0) - f(x^\ast)) + \frac{1}{2}\sum_{i=0}^{k} (A_{i+1} -A_{i})^2\|\nabla f(x_{i})\|_\ast^2}{A_k}.
%\end{align}
